Time and space specifications for stencils

### 2016-03-09 paper.tex
Concerns about operator overloading and sliding in Fortran

\newcommand{\dnote}[1]{\textcolor{darkpurple}{Dom: #1}}

@@

>>>>

\newcommand{\dnote}[1]{\textcolor{darkpurple}{Dom: #1}}
\newcommand{\mnote}[1]{\textcolor{darkgreen}{Mistral: #1}}

@@

\mnote{Few cases that we might like to consider (there are examples
    of each in \#camfort-main Slack channel): 
  \begin{itemize}
    \item Matrix operator overloading $a + b$, where both are arrays
    \item Scalar operator overloading $a + b$, where a is an array b is a 
      scalar. $b$ is added to all.
    \item Sliding. $a = b$ where the dimensionsare $a(1:10)$, $b(2:11)$,
      so the assignment causes shifting.
  \end{itemize}
}
